### 2016-10-21 experiments.tex
new exp and MUSEUM stuff

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering, but, as with previous results \cite{PLDI13} it did not compare well with FPF, and the runtime was much higher.  This tends to confirm the conclusion \cite{PLDI13} that clustering (at least with X-means) does not work well in a setting with extreme disparity in instance counts for faults.  %A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).

@@

There were 96,828 SpiderMonkey mutants, based on 69,634 lines of code in C and header files.  Of these mutants, 12,666 were covered by some failing test case.  Of these mutants, 10,525 survived a basic set of SpiderMonkey quick tests \cite{icst2014}.  Of these mutants, 1,326 (12.6\%) repaired at least one test case.  Figure \ref{jscurves} shows the discovery curves for the mutant repair metric compared to the ideal discovery curve and the best curve from previous work using FPF, which used a normalized Levenshtein distance \cite{lev} over the failure output and test case text \cite{PLDI13}.  The APFD (Average Percent Faults Detected) values shown in the graphs are based on the measure  introduced by Rothermel et al. to evaluate test case prioritization methods \cite{APFD}.  This is a somewhat better summary of results than the raw curve areas used in previous work \cite{PLDI13}.  APFD, as the name suggests, shows the percent of all faults discovered at the ``average'' point on the curve, by comparing the curve's area to an ideal curve, with interpolation\footnote{The details of APFD calculation are slightly involved, and the interpolation and perfect curve are not exact fits for fuzzer taming; nonetheless the basic method summarizes curves fairly well and is standard in the testing literature for similar problems \cite{issta14}.}.

@@

@@

\begin{figure}
{\scriptsize
\begin{code}
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):}
...
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);
<         \} else \{
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);
<         \}
...
<                   a->avail = (jsuword)sp;
<               \}
...
---
>         RESTORE\_SP(fp);
...
{\bf Mutant information:}
Failure repaired by 148 mutants.
...
\#3: delete statement mutant of jsinterp.c:944:

@@

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */
\end{code}
}
\caption{Patch and explanation for fault 115}
%\vspace{-0.18in}
\label{fig:explain}
\end{figure}

@@

\subsubsection{Error Explanation}

@@

The precise form an explanation based on our techniques should take is not clear.  One possibility, suggested by the results here, is a method focused on repairs, but using common coverage changes.  For each repairing mutant, in rank order, the highest ranking coverage changes for that mutant could also be shown, to give an idea of unusual (and potentially localizing) changes induced by repair.

@@

Slicing the tests into 30 random equal-sized groups and comparing with function and line coverage metrics, the difference is statistically validated (Figure \ref{comparegcc}): differences in APFD values are statistically significant between our metric and both PLDI 13 metrics, by Wilcoxon test, with $p < 0.002$, and the mean APFD improvement, even for only 37 tests, exposing only 5-11 faults, is still over 3\%.

@@

In one sense, the discovery curve improvements here are practically useful, but not spectacular.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very best curve chosen after running more than 16 different metrics.  In practice, users do not know ground truth to rank curves, so PLDI 13 does not really give a practical approach to distance metric selection.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, previous work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique.  It also included methods such as comparing output signatures that are inapplicable to differential properties.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work.

@@

 Why does {\bf Repair} perform best in this setting?  It is impossible to be sure, but one  possibility is power to distinguish repairs. If each failure was only repaired by one mutant, MUSEUM and {\bf Repair} would both rank that mutant maximally, and we speculate it would usually be faulty.  But such cases are rare:  for SpiderMonkey the mean/median number of mutants repairing each failure were 90.8 and 78, respectively, and for GCC the mean and median were 54 and 43.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs (since we only use repairs that cause no passing tests to fail).  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.

{\bf Repair} can distinguish such mutants by relying on the onion-ring structure:  when a repair also repairs test cases that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults.  The hypothesis behind {\bf Repair} is that \emph{repairs specific to the fault causing a failure are most likely to modify code involved in the fault itself}.  This seems to be true, when such a repair exists.  If any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.

Finally, in contrast to many previously reported results in fault localization, typically over much simpler programs and faults than subtle compiler semantics bugs, all methods frequently failed to provide a useful localization at all.  In one sense, {\bf Coverage} is the most intriguing method presented here.  While it did not perform nearly as well as {\bf Repair}, it did manage, in many cases, to rank some faulty line highly relative to the extremely large number of statements executed in each failing GCC run (on the order of 50K-100K+ statements).  In future work, we plan to experiment with different methods for weighting frequency of coverage, perhaps using methods from machine learning, or of pruning changed coverage that is not likely to be relevant.  For example, perhaps the {\bf Repair} approach can be applied, and coverage changes present in very distant failures can be removed, though the argument is less clear, since a coverage change isn't directly associated with the onion-ring structure, and does not directly repair a set of failures.  There is much to be done if automated debugging is ever to make the lives of compiler developers easier in most cases \cite{AutoHelp}.

>>>>

We only show results for the first 50 tests in the ranking, and computed areas under curves for the same limit, since it seems very unlikely that a user will examine many more than 50 tests, especially given the decreasing slope of the discovery curves.  In practice, after 50 tests, fixing a few faults and then re-running tests and FPF seems the most likely recourse, and we confirmed that after removing random subsets of faults, our metrics still outperform the previous best.  We applied X-means \cite{xmeans} in an attempt to use clustering, but, as with previous results \cite{PLDI13} it did not compare well with FPF, and the runtime was much higher.  This tends to confirm the conclusion \cite{PLDI13} that clustering is of limited value in fuzzer taming.
% (at least with X-means) does not work well in a setting with extreme disparity in instance counts for faults.  %A further difficulty for our setting is that X-means and most off-the-shelf clustering tools take vectors, not a distance metric.  X-means is using the raw repair data, not weighted by the fact that 0-0 agreement is much less informative than other possible matchings (a Euclidean over 0-1 vectors is just the square root of Hamming distance).

@@

There were 96,828 SpiderMonkey mutants, based on 69,634 lines of code in C and header files.  Of these mutants, 12,666 were covered by some failing test case.  Of these mutants, 10,525 survived a basic set of SpiderMonkey quick tests \cite{icst2014}.  Of these mutants, 1,326 (12.6\%) repaired at least one test case.  Figure \ref{jscurves} shows the discovery curves for the mutant repair metric compared to the ideal discovery curve and the best curve from previous work using FPF, which used a normalized Levenshtein distance \cite{lev} over the failure output and test case text \cite{PLDI13}.  The APFD (Average Percent Faults Detected) values shown in the graphs are based on the measure  introduced by Rothermel et al. to evaluate test case prioritization methods \cite{APFD}.  This is a somewhat better summary of results than the raw curve areas used in previous work \cite{PLDI13}.  APFD, as the name suggests, shows the percent of all faults discovered at the ``average'' point on the curve, by comparing the curve's area to an ideal curve, with interpolation.
%\footnote{The details of APFD calculation are slightly involved, and the interpolation and perfect curve are not exact fits for fuzzer taming; nonetheless the basic method summarizes curves fairly well and is standard in the testing literature for similar problems \cite{issta14}.}.

@@

In order to check whether the improvement is statistically reliable for SpiderMonkey 1.6 faults, we sliced the PLDI 13 tests into 20 randomly selected distinct subsets.  The repair metric had a mean APFD for these subsets (about 90 tests, with a mean of just over 10 distinct faults) 2.85\% better than the mean APFD for the PLDI 13 metric, and the result was statistically significant ($p < 0.05$ by Wilcoxon test).

@@

\begin{comment}
\begin{figure}
{\scriptsize
\begin{code}
{\bf Diff of old ($<$) vs new ($>$) for 115 patch (portion):}
...
<             vp[1] = OBJECT\_TO\_JSVAL(thisp);
<         \} else \{
<             ok = OBJ\_GET\_PROPERTY(cx, thisp, id, \&v);
<         \}
...
<                   a->avail = (jsuword)sp;
<               \}
...
---
>         RESTORE\_SP(fp);
...
{\bf Mutant information:}
Failure repaired by 148 mutants.
...
\#3: delete statement mutant of jsinterp.c:944:

@@

{\bf Coverage change information:}
...
\#6: 5 mutants (3.38\% of repairs) added jsinterp.c:992:
                   a->avail = (jsuword)sp; /* ADDED */
\end{code}
}
\caption{Patch and explanation for fault 115}
%\vspace{-0.18in}
\label{fig:explain}
\end{figure}
\end{comment}

@@

\begin{comment}
\subsubsection{Error Explanation}

@@

The precise form an explanation based on our techniques should take is not clear.  One possibility, suggested by the results here, is a method focused on repairs, but using common coverage changes.  For each repairing mutant, in rank order, the highest ranking coverage changes for that mutant could also be shown, to give an idea of unusual (and potentially localizing) changes induced by repair.
\end{comment}

@@

Slicing the GCC tests into 20 random equal-sized test subsets and comparing with function and line coverage metrics (Figure \ref{comparegcc}) we find that differences in APFD values are statistically significant between our metric and both PLDI 13 metrics, by Wilcoxon test, with $p < 0.0005$, and the mean APFD improvement, even for only 55 tests, exposing only 6-11 faults (mean of 7.75 faults), is more than 3.8\% over either PLDI 13 metric.

@@

In one sense, the discovery curve improvements here are practically very useful, but not exremely large in a relative sense.  The SpiderMonkey curve has an APFD only slightly more than 2\% better than the best result from previous FPF efforts.  For GCC, APFD improves by 6.4\%.  However, the comparison is with the very \emph{best} curve chosen after running more than 16 different metrics.  In practice, users do not know ground truth to rank curves, so PLDI 13 does not really give a practical approach to distance metric selection.  The best methods for different subjects varied widely, even in such difficult-to-understand ways as less-fine-grained coverage providing better results in some cases, but worse in other cases.   In practice, previous work established that FPF could produce good curves, but gave very little useful guidance for choosing a metric for actual use of the technique.  It also included methods such as comparing output signatures that are inapplicable to differential properties.  This paper presents a single curve using a universal metric, and achieves a 2-6\% percentage point improvement over the best of more than 16 different metrics studied in the previous work.  Moreover, the improvement is, for our subject programs, reliable:  choosing random subsets of the full data set, the difference in mean APFD is around 3\%, and statistically significant.

@@

 Why does {\bf Repair} perform best in this setting?  It is impossible to be sure, but one  possibility is power to distinguish repairs. If each failure was only repaired by one mutant, MUSEUM and {\bf Repair} would both rank that mutant maximally, and we speculate it would usually be faulty.  But such cases are rare:  for SpiderMonkey the mean/median number of mutants repairing each failure were 90.8 and 78, respectively, and for GCC the mean and median were 54 and 43.  If there are many repairs for a failure, how can the most important ones be distinguished?  MUSEUM relies on a large set of mutation operators, and assumes that faulty statements will have multiple repairs, compared to non-faulty statements, or that faulty statements will be less likely to cause passing tests to fail when mutated.  Restricting ourselves to cases where {\bf Repair} and MUSEUM both provided a localization, we know that some faulty statement was in a repairing mutant, but that passing tests could not distinguish this mutant  from other repairs (since we only use repairs that cause no passing tests to fail).  Many of the faulty statement repairs (as expected for optimizing compilers) were statement deletions and conditional negations.  For these, it seems unlikely that Proteum would produce more mutants repairing the statement, though perhaps Proteum would create repairs for other statements that cannot be modified into a repair by any of Andrews' operators.  We applied our repair localization to the MUSEUM data set, using the full Proteum mutant set and added MUSEUM-specific mutants, and for all but one of the 8 bugs in the data set, our results were equivalent to those for MUSEUM (in one case our approach fails to produce a localization).

{\bf Repair} can distinguish more repairing mutants by relying on the onion-ring structure:  when a repair also repairs test cases that otherwise do not resemble the failure being localized (in terms of its repairing mutants), {\bf Repair} assumes that repair is general to many different faults.  The hypothesis behind {\bf Repair} is that \emph{repairs specific to the fault causing a failure are most likely to modify code involved in the fault itself}.  This seems to be true, when such a repair exists.  If any repair for a failure modified a faulty statement, {\bf Repair} always ranked it in the top 34 localizations, ranked it in the top 5 in 6 of 10 such cases, and 3 times ranked it 1st.  MUSEUM, in contrast, ranked one such repair 195th, never ranked a fault in its top 3 statements, and only ranked a fault in its top 5 statements twice.  Of course, MUSEUM might be suffering from a lack of mutation operators, but in some cases this is unlikely due to the nature of the repairs.  For the MUSEUM data set, there are no cases with multiple faults for our method to use to further distinguish repairs, so its similarity to MUSEUM in results is not surprising (in this context, our approach is essentially MUSEUM modified to throw out any repairs that cause previously passing tests to fail).

Finally, in contrast to many previously reported results in fault localization, typically over much simpler programs and faults than subtle compiler semantics bugs, all methods frequently failed to provide a useful localization at all.  This is presumably due to the difficulty of compiler bugs:  our approach, and MUSEUM, performed very well on complex multi-lingual faults in the MUSEUM data set.  In one sense, {\bf Coverage} is the most intriguing method presented here.  While it did not perform nearly as well as {\bf Repair}, it did manage, in many cases, to rank \emph{some} faulty line highly relative to the extremely large number of statements executed in each failing GCC run (on the order of 50K-100K+ statements).  In future work, we plan to experiment with different methods for weighting frequency of coverage, perhaps using methods from machine learning, or of pruning changed coverage that is not likely to be relevant.  For example, perhaps the {\bf Repair} approach can be applied, and coverage changes present in very distant failures can be removed, though the argument is less clear, since a coverage change isn't directly associated with the onion-ring structure, and does not directly repair a set of failures.  There is much to be done if automated debugging is ever to make the lives of compiler developers easier in most cases \cite{AutoHelp}.

### 2016-10-21 localizations.tex
new exp and MUSEUM stuff

Another possible advantage over most statistical approaches to
localization, even some recently proposed, more accurate, mutant-based
approaches, is that our methods are not potentially confused in
settings with multiple faults.  Each localization/explanation is based
on a single failing test case, which in most cases fails due to only one
fault.  In fact, other faults help both methods rank localizations.

>>>>

Another advantage over many statistical approaches to
localization is that our methods are not potentially confused in
settings with multiple faults.  Each localization/explanation is based
on a single failing test case, which in most cases fails due to only one
fault.  In fact, other faults help both methods rank localizations.
